---
title: "Program Overview"
execute: 
  echo: false
---

```{r}
#| include: false

# libraries --------------------------------------------------------------------
library(downloadthis)
library(DT)
library(emo)
library(googlesheets4)
library(tidyverse)

# functions --------------------------------------------------------------------
overview_table <- function(x) {
  x |> 
  datatable(
    colnames = NULL,
    rownames = FALSE,
    options = list(
      dom = 't', 
      pageLength = -1, 
      ordering = FALSE,
      columnDefs = list(list(className = 'dt-center', targets = 0))
    ),
  )
}

# data -------------------------------------------------------------------------
isre24_program_overview <- 
  paste0(
    "https://docs.google.com/spreadsheets/d/",
    "1-L884Twe1mh6pdItcBO8QobBRAXgw-RkbinI5QrvEtk"
  ) |> 
  read_sheet() |> 
  mutate(icon = case_when(
    str_detect(event, "Registration") ~ "⏰",
    str_detect(event, "Welcome|Members|Editors|Closing|Industry") ~ "🎤",
    str_detect(event, "Keynote") ~ "🎤️",
    str_detect(event, "Coffee and Tea") ~ "☕",
    str_detect(event, "Parallel Session") ~ "💬",
    str_detect(event, "Lunch") ~ "🥙",
    str_detect(event, "Poster") ~ "📜",
    str_detect(event, "Flash") ~ "⚡"
  )) |> 
  relocate(icon, .before = event)

```

```{r}
download_link(
  link = "../ISRE2024_ProvisionalProgram_20240619.pdf",
  button_label = "Download the Provisional Program Here!",
  button_type = "danger",
  has_icon = TRUE,
  icon = "fa fa-download",
  self_contained = FALSE,
  class = "button_custom"
)
```

<br>

## 17 July

#### Morning & Afternoon 

Pre-conferences:

- [Affective Computing with a special session on Large Language Models](../preconference/list/affective_computing.qmd)
- [Cross-Species Emotion Research](../preconference/list/cross_species.qmd)
- [Emotion Regulation in Online Contexts and Links to Mental Health and Wellbeing](../preconference/list/experience_regulation.qmd)
- [Emotions in Interpersonal Relationships](../preconference/list/emotions_relationships.qmd)
- [Engaging with Other People’s Suffering: Emotion, Empathy, Eudaimonia and Curiosity](../preconference/list/engaging_suffering.qmd)
- [Language and Emotional Development](../preconference/list/emotional_development.qmd)
- [Laughter and Other Non-Verbal Vocalisations](../preconference/list/laughter_workshop.qmd)

#### Evening

**ISRE2024 Welcome Reception, Parliament Buildings**

## 18 July

```{r}
isre24_program_overview |> 
  filter(day == 18) |> 
  select(-day) |> 
  overview_table()
```

#### Evening

**ISRE2024 Early Career Event, QUB Great Hall**

## 19 July

```{r}
isre24_program_overview |> 
  filter(day == 19) |> 
  select(-day) |> 
  overview_table()
```

#### Evening

**ISRE2024 Conference Dinner, Titanic Belfast**

## 20 July

```{r}
isre24_program_overview |> 
  filter(day == 20) |> 
  select(-day) |> 
  overview_table()
```

## Acknowledgements

We would like to thank the many people who have helped in the preparation of the conference.

Dissertation Award judges:

- Phase 1 - Initial Review: Andrea Scarantino, Ronnie de Sousa, Armindo Freitas-Magalhães, Karen Gasper, Manny Gonzalez, Pascal Hot, Elif Sandal Önal, Yoann Stussi, Eric Vanman, Eric Walle, Michelle Yik, and Vanda Zammuner.
- Phase 2 - Detailed Review: Ronnie De Sousa, Manny Gonzalez, and Yoann Stussi.