---
title: "Program Overview"

toc: true
execute: 
  echo: false
  message: false
---

```{r}
#| include: false

# libraries --------------------------------------------------------------------
library(here)
library(downloadthis)
library(DT)
library(googlesheets4)
library(tidyverse)

# functions --------------------------------------------------------------------
overview_table <- function(x) {
  x |> 
    datatable(
      colnames = NULL,
      rownames = FALSE,
      extensions = 'Responsive',
      options = list(
        dom = 't', 
        pageLength = -1, 
        ordering = FALSE,
        columnDefs = list(list(className = 'dt-center', targets = 0))
      ),
      escape = FALSE
    )
}

# data -------------------------------------------------------------------------
isre24_program_overview <- 
  paste0(
    "https://docs.google.com/spreadsheets/d/",
    "1-L884Twe1mh6pdItcBO8QobBRAXgw-RkbinI5QrvEtk"
  ) |> 
  read_sheet() |> 
  mutate(
    event = str_replace_all(event, c(
      "Keynote 1: Yuri Miyamoto" = '<a href="https://www.isre2024.org/keynotes/speakers/Yuri_Miyamoto">Keynote 1: Yuri Miyamoto</a>',
      "Keynote 2: Phoebe Ellsworth" = '<a href="https://www.isre2024.org/keynotes/speakers/Phoebe_Ellsworth">Keynote 2: Phoebe Ellsworth</a>',
      "Keynote 3: Terry Maroney" = '<a href="https://www.isre2024.org/keynotes/speakers/Terry_Maroney">Keynote 3: Terry Maroney</a>',
      "Industry Salon: Michel Valstar" = '<a href="https://www.isre2024.org/program/industry">Industry Salon: Michel Valstar</a>'
    )),
    icon = case_when(
      str_detect(event, "Registration") ~ "⏰",
      str_detect(event, "Welcome|Members|Editors|Closing|Industry") ~ "🎤",
      str_detect(event, "Keynote") ~ "🎤️",
      str_detect(event, "Coffee and Tea") ~ "☕",
      str_detect(event, "Parallel Session") ~ "💬",
      str_detect(event, "Lunch") ~ "🥙",
      str_detect(event, "Poster") ~ "📜",
      str_detect(event, "Flash") ~ "⚡"
  )) |> 
  relocate(icon, .before = event)
```


Gain access to a **mobile-friendly and customizable program**, engage with speakers by asking questions, receive conference tips, and join the community with the Whova app:

[{{< fa mobile >}} Access Whova App Here!](https://whova.com/portal/isrec_202407){.btn .btn-danger .button_custom .btn role="button"}

<center> Or </center>

[{{< fa download >}} Download the Program Here!](../ISRE2024_program.pdf){.btn .btn-danger .button_custom .btn role="button"}

```{r}
# download_link(
#   link = "../ISRE2024_program.pdf",
#   button_label = "Download the Program Here!",
#   button_type = "danger",
#   has_icon = TRUE,
#   icon = "fa fa-download",
#   self_contained = FALSE,
#   class = "button_custom"
# )
```

<br>

Please note that **Shimna: PFC/02/011** is the quiet room during the main ISRE2024 conference 

## 17 July {#july-17}

#### Morning & Afternoon 

Registration on the 17th is in the Great Hall (and then in Whitla Hall during the main conference)

Pre-conferences:

- [Affective Computing with a special session on Large Language Models](../preconference/list/affective_computing.qmd) (Bann: PFC/0G/024)
- [Cross-Species Emotion Research](../preconference/list/cross_species.qmd) (Moyola: PFC/02/017)
- [Emotion Regulation in Online Contexts and Links to Mental Health and Wellbeing](../preconference/list/experience_regulation.qmd) (Shimna: PFC/02/011)
- [Emotions in Interpersonal Relationships](../preconference/list/emotions_relationships.qmd) (Roe: PFC/02/018)
- [Engaging with Other People’s Suffering: Emotion, Empathy, Eudaimonia and Curiosity](../preconference/list/engaging_suffering.qmd) (Farset: PFC/02/025)
- [Language and Emotional Development](../preconference/list/emotional_development.qmd) (Lagan: PFC/02/026)
- [Laughter and Other Non-Verbal Vocalisations](../preconference/list/laughter_workshop.qmd) (Council Chamber)

#### Evening: ISRE2024 Welcome Reception for all ISRE attendees, Parliament Buildings

- 18:15 Buses departure from the QUB campus to the Northern Ireland Assembly 
- 19:00 - 22:00 Welcome Reception 

## 18 July {#july-18}

```{r}
isre24_program_overview |> 
  filter(day == 18) |> 
  select(-day) |> 
  overview_table()
```

See [here](days/july_18.qmd) for more details on the day.

#### Evening

**19:00 ISRE2024 Early Career Event, QUB Great Hall**

## 19 July {#july-19}

```{r}
isre24_program_overview |> 
  filter(day == 19) |> 
  select(-day) |> 
  overview_table()
```

See [here](days/july_19.qmd) for more details on the day.

#### Evening

**ISRE2024 Conference Dinner, Titanic Belfast**

## 20 July {#july-20}

```{r}
isre24_program_overview |> 
  filter(day == 20) |> 
  select(-day) |> 
  overview_table()
```

See [here](days/july_20.qmd) for more details on the day.

## Acknowledgements

We would like to thank the many people who have helped in the preparation of the conference.

Dissertation Award judges:

- Phase 1 - Initial Review: Andrea Scarantino, Ronnie de Sousa, Armindo Freitas-Magalhães, Karen Gasper, Manny Gonzalez, Pascal Hot, Elif Sandal Önal, Yoann Stussi, Eric Vanman, Eric Walle, Michelle Yik, and Vanda Zammuner.
- Phase 2 - Detailed Review: Ronnie De Sousa, Manny Gonzalez, and Yoann Stussi.

```{r}
#| include: false
# 
# isre24_program_communications <-
#   read_sheet("https://docs.google.com/spreadsheets/d/1IXNmqqwtPi70zxuf4q6QTpIsFi4anOuSm4RZySt_m7A")
# 
# PSSlot_Track <- isre24_program_communications |> 
#   select(PSSlot, Track) |> 
#   distinct() |> 
#   filter(PSSlot != "Poster Session")
# 
# walk2(PSSlot_Track$PSSlot, PSSlot_Track$Track, ~quarto::quarto_render(
#   input = here("program/tracks.qmd"),
#   execute_params = list("PSSlot" = .x, "Track" = .y),
#   output_file = glue::glue("{snakecase::to_any_case(.x)}_{.y}.html")
# ))
# 
# PSSlot_Track <- isre24_program_communications |> 
#   filter(PSSlot == "Poster Session") |> 
#   select(PosterSession) |> 
#   distinct()
# 
# walk(PSSlot_Track$PosterSession, ~quarto::quarto_render(
#   input = here("program/poster.qmd"),
#   execute_params = list("PosterSession" = .x),
#   output_file = glue::glue("{snakecase::to_any_case(.x)}.html")
# ))
```

